Supplement to Automatic Matching of Bullet Lands

### 2016-11-30 imaging-paper.Rnw
Fix paper building on linux

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read_x3p(images[5]), name = images[5], x = 100)
subLOFx2 <- processBullets(read_x3p(images[7]), name = images[7], x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y + 23*1.5625 # working now!!!
lofX <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read_x3p(images[5]), name = images[5], x = 100)
subLOFx2 <- processBullets(read_x3p(images[7]), name = images[7], x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y - min(subLOFx1$y)
subLOFx2$y <- subLOFx2$y - min(subLOFx2$y)
ccf <- ccf(subLOFx1$resid, subLOFx2$resid, lag.max=100, plot=FALSE)
lag <- ccf$lag[which.max(ccf$acf)]
subLOFx1$y <- subLOFx1$y - lag*1.5625 
lofY <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

  subLOFx1 <- processBullets(read_x3p(images[5]), name = images[5], x = 100)
  subLOFx2 <- processBullets(read_x3p(images[7]), name = images[7], x = 100)
  lof <- rbind(subLOFx1, subLOFx2)

>>>>

im1 <- "images/Hamby (2009) Barrel/bullets/Br1 Bullet 1-5.x3p"
im2 <- "images/Hamby (2009) Barrel/bullets/Br1 Bullet 2-1.x3p"

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read_x3p(im1), name = im1, x = 100)
subLOFx2 <- processBullets(read_x3p(im2), name = im2, x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y + 23*1.5625 # working now!!!
lofX <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read_x3p(im1), name = im1, x = 100)
subLOFx2 <- processBullets(read_x3p(im2), name = im2, x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y - min(subLOFx1$y)
subLOFx2$y <- subLOFx2$y - min(subLOFx2$y)
ccf <- ccf(subLOFx1$resid, subLOFx2$resid, lag.max=100, plot=FALSE)
lag <- ccf$lag[which.max(ccf$acf)]
subLOFx1$y <- subLOFx1$y - lag*1.5625 
lofY <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

  subLOFx1 <- processBullets(read_x3p(im1), name = im1, x = 100)
  subLOFx2 <- processBullets(read_x3p(im2), name = im2, x = 100)
  lof <- rbind(subLOFx1, subLOFx2)

### 2016-11-30 imaging-supplement.Rnw
Fix paper building on linux

crosscuts <- seq(100, 400, by = 50)
lof <- processBullets(read_x3p(paths[5]), name = scrubPath(paths[5]), x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

>>>>

im1 <- "images/Hamby (2009) Barrel/bullets/Br1 Bullet 1-5.x3p"

crosscuts <- seq(100, 400, by = 50)
lof <- processBullets(read_x3p(im1), name = scrubPath(im1), x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)
